# Introduction


# Grammar of Graphics


# R packages

```{r, comment=NA, message=FALSE, warning=FALSE}
library(tidyverse)
library(GGally) # Matrix plots
#devtools::install_github("EvaMaeRey/ggxmean")
library(ggxmean)
#devtools::install_github("davidsjoberg/ggsankey")
library(ggsankey)
```

# Data sets

```{r}
#install_github("thiyangt/elephants")
library(elephants)
data("elephants")

```

# Small dataset

```{r}
elephants.subset.100 <- elephants |> sample_n(100)
```


# Geometris: `geom` - Qualitative data visualisation 

## geom_bar

```{r, echo=TRUE}
ggplot(elephants, aes(y = Age_Category)) + 
  geom_bar()

```

```{r, echo=TRUE}
ggplot(elephants, aes(y = Age_Category, fill=Category)) + 
  geom_bar()
```

```{r, echo=TRUE}
ggplot(elephants, aes(y=Age_Category, fill = Category)) +
  geom_bar(position = "dodge")
```

## geom_col

Before using `geom_col`, you need to create a summary table of counts or you can apply `geom_col` for a summary table already given.

```{r, echo=FALSE}
elephants_counts <- elephants |> 
  group_by(Age_Category) |> 
  summarise(n = n())
elephants_counts
```



```{r, echo=FALSE}
ggplot(elephants_counts, aes(x = Age_Category, y=n)) + 
  geom_col()
```


# Quantitative data visualisation

## geom_histogram

```{r, echo=FALSE}
ggplot(elephants, aes(x = Weight)) + 
  geom_histogram(col="white")

```


## geom_density


```{r, echo=FALSE}
ggplot(elephants, aes(x = Weight)) + 
  geom_density()

```


## geom_boxplot

```{r, echo=FALSE}
ggplot(elephants, aes(y = Weight)) + 
  geom_boxplot()

```

```{r, echo=FALSE}
ggplot(elephants, aes(y = Weight)) + 
geom_boxplot(outlier.colour="black", outlier.shape=16,
             outlier.size=2, notch=TRUE)

```






# Qualitative and qualitative data visualisation

## geom_boxplot

```{r}
ggplot(elephants, aes(y = Weight, x=Category)) + geom_boxplot()
```

## geom_signif

```{r}
ggplot(elephants, aes(y = Weight, x=Category)) + geom_boxplot() + ggsignif::geom_signif()
```

## geom_violin

```{r, echo=FALSE}
ggplot(elephants, aes(y = Weight, x=Category)) + 
  geom_violin()

```

Without trimming

```{r, echo=FALSE}
ggplot(elephants, aes(y = Weight, x=Category)) + 
  geom_violin(trim=FALSE)

```


Draw quantiles

```{r, echo=FALSE}
ggplot(elephants, aes(y = Weight, x=Category)) + 
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))

```

# Quantitative and quantitative data visualisation

## geom_point

```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_point()

```

## geom_dl


```{r, echo=FALSE}
library(directlabels)
ggplot(elephants, aes(y = Height, x=Weight, col=Category)) + 
  geom_point() +
  geom_dl(aes(label=Category),method="smart.grid")
```

## geom_encircle

```{r, echo=FALSE}
library(ggalt)
ggplot(elephants, aes(y = Height, x=Weight, col=Category)) + 
 geom_encircle(aes(fill =Category), s_shape=0.2, expand=0.01 , alpha=0.4) 
```

`geom_encircle` with `geom_point`

```{r, echo=FALSE}
library(ggalt)
ggplot(elephants, aes(y = Height, x=Weight, col=Category)) + 
  geom_point() + geom_encircle(aes(fill =Category), s_shape=0.2, expand=0.01 , alpha=0.4) 
```

## geom_mark_circle

```{r, echo=FALSE}
library(ggforce)
ggplot(elephants, aes(y = Height, x=Weight)) +
  geom_mark_circle(aes(fill = Category, label = Category),
                   con.cap = 0) 
```

With geom_point

```{r, echo=FALSE}
library(ggforce)
ggplot(elephants, aes(y = Height, x=Weight)) +
  geom_mark_circle(aes(fill = Category, label = Category),
                   con.cap = 0) +
  geom_point()


```

## geom_delaunay_tile

```{r}
ggplot(elephants.subset.100, aes(y = Height, x=Weight)) +
  ggforce::geom_delaunay_tile(alpha = 0.5, colour = 'red')
```

## geom_label_repel

```{r}
ggplot(elephants.subset.100, aes(y = Height, x=Weight)) +
  geom_point() +
  ggrepel::geom_label_repel(aes(y = Height, x=Weight, 
                                label = rownames(elephants.subset.100)),
                                fontface = 'bold', color = 'red',
                                box.padding = unit(0.40, "lines"),
                                point.padding = unit(0.6, "lines"),
                                segment.color = 'grey50'
  )
```

## geom_smooth

```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_smooth()

```

```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_smooth(method=lm)

```

```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_smooth(method = lm, formula = y ~ splines::bs(x, 4))

```

## geom_lm


```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_lm()
```


## geom_density_2d

```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_density_2d()

```

## geom_density_2d_filled

```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_density_2d_filled()

```



## geom_density_ridges

Here the `y` variable should be qualitative and the `x` variable should be quantitiative.


```{r, echo=FALSE}
library(ggridges)
ggplot(elephants, aes(y=Category, x = Height)) + 
    geom_density_ridges()

```




# Others

## geom_function

```{r}
ggplot() + xlim(c(-1,1)) + geom_function(fun=cos, colour="red",lwd=1, linetype=1)

```




# Grammar of graphics extensions


With all variables

## ggpairs


```{r, echo=TRUE, warning=FALSE, message=FALSE}
GGally::ggpairs(elephants)
```

With only numeric variables

```{r, echo=TRUE, warning=FALSE, message=FALSE}
elephants.numeric <- elephants |> select_if(is.numeric)     
GGally::ggpairs(elephants.numeric)
```

Colour the points according to category

```{r, echo=TRUE, warning=FALSE, message=FALSE}
elephants.numeric <- elephants |> select_if(is.numeric) 
elephants.numeric$Category <- elephants$Category
GGally::ggpairs(elephants.numeric, aes(col=Category))
```


