# A: geom_a...

## geom_abline{#abline}

**Package: ** ggplot2 [@R-ggplot2]

**Book: **

**Description: ** Draw a straight line ($Y=mX+c$) for a given slope ($m$)  and intercept ($c$).

**Understandable aesthetics:** alpha, colour, linetype, linewidth

**Statistics layer(s):**

**See also: ** [geom_point](#point), [geom_vline](#vline), [geom_hline](#hline)

**Example:**

```{r, fig.cap="Illustration of (A) geom_abline and (B) use of geom_point and geom_abline both"}
abline <- ggplot(worldbankdata, aes(y = Cooking, x=Electricity)) +  geom_abline(intercept = 0, slope = 1) + 
  labs(title="A: `geom_abline` only") +
  theme(aspect.ratio = 1)

pointabline <- ggplot(worldbankdata, aes(y = Cooking, x=Electricity)) + 
  geom_point() + 
  geom_abline(intercept = 0, slope = 1) + 
  labs(title="B: `geom_point + geom_abline` both") +
  theme(aspect.ratio = 1)

library(patchwork)
abline | pointabline
```

## geom_area{#area}

**Package: ** ggplot2 [@R-ggplot2]

**Description: **Create an area plot. This cover the space between x-axis and line that connects the data points.

**Understandable aesthetics:** alpha, colour, linetype, linewidth

**Statistics layer(s):**



**See also: ** [geom_line](#line), [geom_ribbon](#ribbon)

```{r, fig.cap="Illustration of geom_area"}
colombo <- srilanka_weekly_data |>
  filter(district == "Colombo")
ggplot(data=colombo, aes(x=start.date, y=cases)) + 
  geom_area()
```
