# B: geom_b...

## geom_bar

**Package: ** ggplot2 [@R-ggplot2]

**Description: ** Draw a bar proportional to the specified number. For example, number of cases or user defined number.

**Statistics layer(s): ** 

  `stat_count` - This the default statistics layer. It counts number of cases in each group. 
  
  `stat_identify` - It plots the data as it is.

**See also: ** [geom_col](#col)

### With count 

```{r, fig.cap="Illustration of geom_bar to create a bar chart"}
ggplot(elephants, aes(y = Age_Category)) + 
  geom_bar()

```

```{r, fig.cap="Illustration of geom_bar to create a stacked bar chart"}
ggplot(elephants, aes(y = Age_Category, fill=Category)) + 
  geom_bar()
```

```{r, fig.cap="Illustration of geom_bar to create a cluster bar chart"}
ggplot(elephants, aes(y=Age_Category, fill = Category)) +
  geom_bar(position = "dodge")
```

```{r, fig.cap="Illustration of geom_bar to create a cluster bar chart"}
ggplot(elephants, aes(y=Age_Category, fill = Category)) +
  geom_bar(position = "dodge")
```

### With identity

```{r}
dfbar <- data.frame(class=c("A", "B"),  income = c(100, 200))
ggplot(dfbar, aes(class, income)) +
  geom_bar(stat="identity")
```

## geom_bin_2d

**Package: ** ggplot2 [@R-ggplot2]

**Description: ** Divides the Cartesian plane created by x-variable and y-variable into rectangles, counts the number of observations in each rectangle. Only the observations with rectangles are filled according to the number ofobservations.

**Understandable aesthetics: ** x, y, fill, group

**Statistics layer(s): ** 


**See also: ** [geom_bin2d](#bin2d), [geom_point](#point)

```{r, fig.cap="Illustration of using geom_bin_2d"}
ggplot(elephants.subset.100, aes(y = Height, x=Fore_Feet_Circumference)) +
  geom_bin_2d() + 
  theme(aspect.ratio = 1)
```

```{r, fig.cap="Illustration of changing bins in geom_bin_2d"}
ggplot(elephants.subset.100, aes(y = Height, x=Fore_Feet_Circumference)) +
  geom_bin_2d(bins=20) + 
  theme(aspect.ratio = 1)
```

## geom_bin2d


**Package: ** ggplot2 [@R-ggplot2]

**Description: ** Divides the Cartesian plane created by x-variable and y-variable into rectangles, counts the number of observations in each rectangle. Only the observations with rectangles are filled according to the number ofobservations.

**Understandable aesthetics: ** x, y, fill, group

**Statistics layer(s): ** 


**See also: ** [geom_bin_2d](#bin_2d), [geom_point](#point)

**Example:**

```{r, fig.cap="Illustration of using geom_bin_2d"}
ggplot(elephants.subset.100, aes(y = Height, x=Fore_Feet_Circumference)) +
  geom_bin2d() + 
  theme(aspect.ratio = 1)
```


## geom_blank

**Package: ** ggplot2 [@R-ggplot2]

**Description: ** Draws nothing.

## geom_boxplot


**Package: ** ggplot2 [@R-ggplot2]

**Description: ** Draw a bar proportional to the specified number. For example, number of cases or user defined number.

**Statistics layer(s): ** 

  `stat_boxplot` - This the default statistics layer. This computes minimum, maximum, median, first quartile ($Q1$), third quartile ($Q3$), upper whisker extends up to $Q3 + 1.5 \times IQR$ and lower whisker extends up to $Q1 - 1.5 \times IQR$, where $IQR = Q3 - Q1$. In a notched box plot, it creates 95\% confidence interval for mean.
  

**See also: ** [geom_col](#col)

```{r, fig.cap="Illustration of using geom_boxplot"}
ggplot(elephants, aes(y = Weight)) + 
  geom_boxplot()
```

```{r, fig.cap="Illustration of using geom_boxplot with changing outliers and adding a notch to create notched box plot."}
ggplot(elephants, aes(y = Weight)) + 
geom_boxplot(outlier.colour="black", outlier.shape=16,
             outlier.size=2, notch=TRUE)

```




