# C: geom_c...

## geom_col

Before using `geom_col`, you need to create a summary table of counts or you can apply `geom_col` for a summary table already given.

```{r, echo=FALSE}
worldbankdata |>
  filter(Year == 2021) |>
  group_by(Income) |>
  summarise(n = n()) |>
  ggplot(aes(x = Income, y = n)) + 
  geom_col()

```





## geom_col_pattern{#col_pattern}

**Package: ** ggpattern [@R-ggpattern]

**Description: ** Fill columns with a pattern. User can map a variable for pattern or set a pattern.

**Understandable aesthetics:** x, y, pattern, fill, colour 

**Statistics layer(s):**



**See also: ** [geom_line](#line), [geom_ribbon](#ribbon)

```{r, fig.cap="Illustration of geom_col_pattern"}
worldbankdata |>
  filter(Year == 2021) |>
  group_by(Income) |>
  summarise(n = n()) |>
  ggplot(aes(x = Income, y = n)) + 
  geom_col_pattern( pattern = 'stripe',
    fill    = 'white',
    colour  = 'black')
```

```{r, eval=FALSE}
worldbankdata |>
  filter(Year == 2021) |>
  group_by(Income) |>
  summarise(n = n()) |>
  ggplot(aes(x = Income, y = n)) + 
  ggpattern::geom_col_pattern(aes(pattern=Income))
```

