# L: geom_l...

## geom_label

**Package: ** ggplot2 [@R-ggplot2]

**Description: **  Thisis used to add labeled text to a plot. It allows you to annotate specific data points or regions in your plot with text labels. This also draws a rectangle around the text.

**Understandable aesthetics:** label, fill(controls the background colour of the label) , colour, fontface

**Statistics layer(s):** count

**See also: ** [geom_text](#text), [geom_label_repel](#label_repel)

```{r, fig.cap="A basic example of how geom_label can be used."}

```


## geom_label_repel

```{r}
ggplot(elephants.subset.100, aes(y = Height, x=Weight)) +
  geom_point() +
  ggrepel::geom_label_repel(aes(y = Height, x=Weight, 
                                label = rownames(elephants.subset.100)),
                                fontface = 'bold', color = 'red',
                                box.padding = unit(0.40, "lines"),
                                point.padding = unit(0.6, "lines"),
                                segment.color = 'grey50'
  )
```


## geom_lm


```{r, echo=FALSE}
ggplot(elephants, aes(y = Height, x=Weight)) + 
  geom_lm()
```