# A {#sec-a}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
data("happiness_gdp_income")
```



## geom_abline{#abline}

**Package**

ggplot2 [@ggplot2]

**Description**

Description Draw a straight line ($Y=mX+c$) for a given slope ($m$)  and intercept ($c$).

**Understandable aesthetics**

Unlike most other geoms, `geom_abline` does not depend on the x and y variables that we map for the main plot. `geom_abline` has its own independent characteristics: `intercept` and `slope`.


**See also**

 [geom_point](#point), [geom_vline](#vline), [geom_hline](#hline)

**Example**

```{r, warning=FALSE, message=FALSE}
a1 <- ggplot() +
  geom_abline(intercept = 0, slope = 1) +
  labs(title = "a1: geom_abline only") +
  theme(aspect.ratio = 1)
a2 <- ggplot(happiness_gdp_income, aes(y =HappinessScore2016, x = HappinessScore2015)) +
  geom_abline(intercept = 0, slope = 1) +
  geom_point() +
  labs(title = "a2: geom_abline \n and geom_point") +
  theme(aspect.ratio = 1)
a1 | a2
```


## geom_alluvium{#alluvium}

**Package**

ggalluvial[@brunson2019package; @brunson2020ggalluvial]

**Description**

Create alluvial plot. An alluvial plot is a type of diagram that is particularly useful for visualizing categorical data and the flow or transition between different categorical variables over multiple stages or categories.

**Understandable aesthetics**

*required aesthetics*

**Option 1 (See Example 1)**

`axis1` - First axis

`axis2` - Second axis

`y` -  Counts to determines the height/weight of the alluvium

**Option 2 (alluvium time-series plot, see Example 2)**

`x` - Time variable determining the horizontal axis

`y` - Determines the height/size of the flow

`alluvium` - According to this variable it defines the flow across the years. In our Example 2, Bangladesh and Sri Lanka.
 


*optional aesthetics*

`alpha`, `colour`, `fill`, `linetype`, `size`, `group` (group is used internally; arguments are ignored)


**See also**

[geom_stratum](#stratum), [geom_flow](#flow), [geom_line](#line) [geom_lode](#lode)

**Example 1**

This example shows the distribution of income level categories in 2021 and 2022 in the regions `Sub-Saharan Africa` and `Latin America & Caribbean`.

```{r alluvial, fig.width=10,fig.height=10, warning=FALSE, message=FALSE}
library(ggalluvial)
freq.table <- worldbankdata |>
  select(Country, Region, Year, Income) |>
  filter(Year > 2020) |>
  filter(Region %in% c("Sub-Saharan Africa", "Latin America & Caribbean")) |>
  group_by(Region, Year, Income) |>
  summarise(n = n()) |>
  drop_na()
freq.table

a1 <- freq.table |>
  ggplot(aes(y = n, axis1 = Income, axis2 = Region)) +
  geom_alluvium(aes(fill = as.factor(Year)), width = 1 / 12) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "a1: geom_alluvium only")

a2 <- freq.table |>
  ggplot(aes(y = n, axis1 = Income, axis2 = Region)) +
  geom_alluvium(aes(fill = as.factor(Year)), width = 1 / 12) +
  geom_stratum(width = 1 / 12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +  scale_fill_brewer(palette = "Dark2") +
  labs(title = "a2: geom_alluvium, \n geom_stratum and geom_label")
a1 / a2
```

**Example 2**


```{r}
p1 <- worldbankdata |>
  filter(Country %in% c("Bangladesh", "Sri Lanka"),
         Year >= 2013, Year <= 2021) |>
  ggplot(aes(x = Year,
             y = Electricity,
             alluvium = Country,
             stratum = Country,
             fill = Country)) +
  geom_alluvium(alpha = 0.6) +
  #geom_stratum(width = 0.4, color = "black") +
  scale_x_continuous(breaks = 2013:2021) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(title = "a1: geom_alluvium only",
       x = "Year",
       y = "Electricity",
       fill = "Country")
p2 <-  worldbankdata |>
  filter(Country %in% c("Bangladesh", "Sri Lanka"),
         Year >= 2013, Year <= 2021) |>
  ggplot(aes(x = Year,
             y = Electricity,
             alluvium = Country,
             stratum = Country,
             fill = Country)) +
  geom_alluvium(alpha = 0.6) +
  geom_stratum(width = 0.4, color = "black") +
  scale_x_continuous(breaks = 2013:2021) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(title = "a2: geom_alluvium and geom_stratum",
       x = "Year",
       y = "Electricity",
       fill = "Country")
p1/p2
```

## geom_arc

**Package**

ggforce[@ggforce]

**Description**

Draw a circle or a segment of a circle.

**Understandable aesthetic**

*required aesthetics*

`x0` - x coordinate of the center of the circle

`y0` - y coordinate of the center of the circle

`r` - radius, 

`start` -  starting point of the circumference

`end` - end point of the circumference

*optional aesthetics*

`color`, `linewidth`, `linetype`, `alpha`, `lineend`

**The statistical transformation to use on the data for this layer**

`stat_arc`

**See also**

[geom_arc2](#arc2), [geom_arc_bar](#arcbar)

**Example**

In the example below, geom_arc() is applied twice to show how the black arc forms the full circle, while the red arc highlights a specific portion of that circle. 

```{r arc, warning=FALSE, message=FALSE}
library(ggforce)
ggplot() +
  geom_arc(aes(x0 = 0, y0 = 0, r = 8, start = 1, end = 8)) +
  geom_arc(aes(x0 = 0, y0 = 0, r = 8, start = 1, end = 5), col = "red", size = 2) +
  theme(aspect.ratio = 1)
```



## geom_arc_bar{#arcbar}

**Package**

ggforce[@ggforce]

**Description**

To draw pie chart and donut chart defining centre point, a radius and a start and end angle.

**Understandable aesthetic**

*required aesthetics*

`x0` - x-coordinate of the center of the pie chart

`y0` - y coordinate of the center of the circle

`r0` - Inner radius of the arc bar. If it is 0, the chart becomes a pie chart (no hole)

`r` - Outer radius of the pie chart slices

`amount` - Determines the size (angle) of each slice. Larger counts produce larger slices

`fill` - Fill colour for each slice

`exploid` - Moves selected slices slightly outward from the center to highlight them

*optional aesthetics*

`color`, `linewidth`, `linetype`, `alpha`, `lineend`

**The statistical transformation to use on the data for this layer**

`stat_arc`

**See also**

[geom_arc](#arc), [geom_arc_bar](#arcbar)

**Example**


```{r, warning=FALSE, message=FALSE, fig.height=10, fig.width=5}
# Count observations in each Income category
df <- worldbankdata |>
  filter(!is.na(Region)) |>
  count(Region, name = "count") |>
  mutate(
    Region = Region,
    focus1 = 0,
    focus2 = c(0.2, 0, 0, 0, 0, 0, 0)
  )
df
# Pie chart
a1 <- ggplot(df) +
  geom_arc_bar(aes(
    x0 = 0, y0 = 0,
    r0 = 0, r = 2,
    amount = count,
    fill = Region,
    explode = focus1
  ), stat = "pie") +
  scale_fill_brewer(palette = "Dark2") +
  theme(aspect.ratio = 1, legend.position = "bottom") +
  labs(fill = "Regions", title = "a1: with exploid = 0")

a2 <- ggplot(df) +
  geom_arc_bar(aes(
    x0 = 0, y0 = 0,
    r0 = 0, r = 2,
    amount = count,
    fill = Region,
    explode = focus2
  ), stat = "pie") +
  scale_fill_brewer(palette = "Dark2") +
  theme(aspect.ratio = 1, legend.position = "bottom") +
  labs(fill = "Regions", title = "a2: with exploid = 0.2 for East Asia and Pacific")
a1/a2
```




## geom_area{#area}

**Package**

ggplot2 [@ggplot2]

**Description**

Create an area plot. This cover the space between x-axis and line that connects the data points.

**Understandable aesthetics**

*required aesthetics*

`x`, `y`

*optional aesthetics*

`alpha`, `colour`, `fill`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)

**Example**

```{r area, warning=FALSE, message=FALSE}
a1 <- worldbankdata |>
  filter(Country == "Bangladesh") |>
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x = Year, y = Electricity)) +
  geom_area(alpha = 0.5) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_continuous(breaks = 2013:2021) +
  labs(title = "a1: geom_area only")

a2 <- worldbankdata |>
  filter(Country == "Bangladesh") |>
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x = Year, y = Electricity)) +
  geom_area(alpha = 0.5) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_continuous(breaks = 2013:2021) +
  geom_point(col = "red") +
  labs(title = "a2: geom_area \n and geom_point")
a1 | a2
```

## geom_arima

**Package**

ggdemetra 

**Example**

```{r, warning=FALSE, message=FALSE}
library(ggdemetra)
 worldbankdata |>
  filter(Country == "Bangladesh") |>
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x = Year, y = Electricity)) +
  geom_line() + 
  #geom_sa(color = "#155692", message = FALSE) +
  geom_arima(geom = "label",
               x_arima = - Inf, y_arima = -Inf, 
               vjust = -1, hjust = -0.1,
               message = FALSE)
  
```

## geom_arrow{#arrow}

**Package**

metR [@metR]

**Description**

Draws directional arrows (like vectors) on a plot, which can represent directions or flows — such as wind directions, movement, or gradients. The arrow from (x, y) and pointing in the direction (dx, dy) (vector components).


**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
 `arrow,type`, `arrow.angle`, `arrow.length`, `arrow.ends`, `arrow.type`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
### Example
  
```{r warning=FALSE, message=FALSE}
library(metR)
data <- tibble::tibble(
  x = c(10, 20, 30, 40, 50),      # Longitude or X-coordinates
  y = c(1, 2, 3, 4, 5),           # Latitude or Y-coordinates
  dx = c(1, 0, -1, 0, 1),         # Wind direction components (change in X)
  dy = c(1, -1, 0, 1, 0)          # Wind direction components (change in Y)
)

ggplot(data, aes(x = x, y = y)) +
  geom_point(color = "#1b9e77", size = 3) +  
  geom_arrow(aes(dx = dx, dy = dy), color = "#d95f02", size = 1, arrow.type = "closed") +
  labs(title = "Wind Directions at Different Locations", x = "Longitude", y = "Latitude")
```

## geom_ash{#ash}

**Package**

ggformula [@ggformula]



**Description**

Plot Average Shifted Histogram (ASH). The ASH is a nonparametric probability density estimator derived from a collection of histograms.

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
 `color`, `fill`, `bins`, `alpha`, `size`


**See also**

[geom_histogram](#histogram), [geom_density](#density)
  
**Example**


```{r, warning=FALSE, message=FALSE}
#| warning: false
#| message: false
#| fig.width: 10
#| fig.height: 5
library(ggformula)
p1 <- worldbankdata |>
  filter(Income == "LM") |>
  ggplot(aes(x = Electricity)) +
   geom_ash(bins = 20, color = "#d95f02") +   labs(title="Average Shifted Histogram")
p2 <- worldbankdata |>
  filter(Income == "LM") |>
  ggplot(aes(x = Electricity)) +
  geom_histogram(aes(y = stat(density)), color = "black", fill = "gray") +
   geom_ash(bins = 20, color = "#d95f02") + labs(title = "Histogram and Average Shifted Histogram")
p1|p2
```

## geom_autodensity

**Package**

ggforce [@ggforce]

**Description**

A matrix-style (commonly from GGally package) visualizations to automatically display variable distributions on diagonal panels, handling both continuous and discrete data while simplifying the mapping of panel variables.


**Understandable aesthetics**

*required aesthetics*
  
  `data`


*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_density](#density), [geom_histogram](#histogram), [geom_autohistogram](#autohistogram), [geom_autopoint](#autopoint),

  
**Example**

```{r}
library(ggplot2)
library(GGally)

# Select numeric variables
df <- happiness_gdp_income |>
  select("HappinessScore2015", "HappinessScore2016", "HappinessScore2017")


ggplot(df) +
  facet_matrix(
    vars(
      HappinessScore2015, 
      HappinessScore2016, 
      HappinessScore2017
    ),
    layer.diag = 1
  ) +
  geom_autodensity()
```

## geom_autohistogram

**Package**

ggforce [@ggforce]

**Description**

**Understandable aesthetics**

*required aesthetics*
  
  `data`


*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_histogram](#histogram), [geom_auotodensity](#autodensity), [geom_auotpoint](#autopoint)
  
**Example**

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(GGally)

# Prepare dataset
df <- happiness_gdp_income %>%
  select(HappinessScore2015, HappinessScore2016, HappinessScore2017,
         GDPpercapita2015) %>%
  rename(GDPpercapita = GDPpercapita2015) %>%
  # Create income category
  mutate(IncomeCategory = case_when(
    GDPpercapita < 1.2 ~ "Low",
    GDPpercapita >= 1.2 & GDPpercapita < 1.4 ~ "Medium",
    GDPpercapita >= 1.4 ~ "High"
  )) %>%
  mutate(
    IncomeCategory = factor(IncomeCategory, levels = c("Low", "Medium", "High")),
    # Create discrete happiness scores by rounding
    HappinessScore2015_discrete = factor(round(HappinessScore2015)),
    HappinessScore2016_discrete = factor(round(HappinessScore2016)),
    HappinessScore2017_discrete = factor(round(HappinessScore2017))
  )

# Plot facet matrix using discrete happiness scores
ggplot(df, aes(x = .panel_x, fill = IncomeCategory)) +
  facet_matrix(
    vars(HappinessScore2015_discrete, HappinessScore2016_discrete, HappinessScore2017_discrete),
    layer.diag = 1,
    grid.y.diag = FALSE
  ) +
  geom_autohistogram(alpha = 0.7, position = "dodge") +  # diagonal histograms
  geom_autopoint(alpha = 0.6, aes(color = IncomeCategory)) +  # off-diagonal scatterplots
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  theme_minimal() +
  labs(
    fill = "Income Category",
    color = "Income Category",
    title = "Discrete Happiness Scores by Income Category",
    x = "",
    y = ""
  )
```
  
## geom_autopoint

**Package**

ggplot2 [@ggplot2]

**Description**

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
**Example**

## geom_axis_hive

**Package**

ggplot2 [@ggplot2]

**Description**

**Understandable aesthetics**

*required aesthetics*
  
  `data`


*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
**Example**


