# A {#sec-a}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
data("happiness_gdp_income")
```



## geom_abline{#abline}

**Package**

ggplot2 [@ggplot2]

**Description**

Description Draw a straight line ($Y=mX+c$) for a given slope ($m$)  and intercept ($c$).

**Understandable aesthetics**

Unlike most other geoms, `geom_abline` does not depend on the x and y variables that we map for the main plot. `geom_abline` has its own independent characteristics: `intercept` and `slope`.


**See also**

 [geom_point](#point), [geom_vline](#vline), [geom_hline](#hline)

**Example**

```{r, warning=FALSE, message=FALSE}
a1 <- ggplot() +
  geom_abline(intercept = 0, slope = 1) +
  labs(title = "a1: geom_abline only") +
  theme(aspect.ratio = 1)
a2 <- ggplot(happiness_gdp_income, aes(y =HappinessScore2016, x = HappinessScore2015)) +
  geom_abline(intercept = 0, slope = 1) +
  geom_point() +
  labs(title = "a2: geom_abline \n and geom_point") +
  theme(aspect.ratio = 1)
a1 | a2
```


## geom_alluvium{#alluvium}

**Package**

ggalluvial[@brunson2019package; @brunson2020ggalluvial]

**Description**

Create alluvial plot. An alluvial plot is a type of diagram that is particularly useful for visualizing categorical data and the flow or transition between different categorical variables over multiple stages or categories.

**Understandable aesthetics**

*required aesthetics*

`x`, `y`, `ymin`, `ymax`, 


*optional aesthetics*

`alpha`, `colour`, `fill`, `linetype`, `size`, `group` (group is used internally; arguments are ignored)


**See also**

[geom_stratum](#stratum), [geom_flow](#flow), [geom_lode](#lode)

**Example**

This example shows the distribution of income level categories in 2021 and 2022 in the regions `Sub-Saharan Africa` and `Latin America & Caribbean`.

```{r alluvial, fig.width=10,fig.height=10, warning=FALSE, message=FALSE}
library(ggalluvial)
freq.table <- worldbankdata |>
  select(Country, Region, Year, Income) |>
  filter(Year > 2020) |>
  filter(Region %in% c("Sub-Saharan Africa", "Latin America & Caribbean")) |>
  group_by(Region, Year, Income) |>
  summarise(n = n()) |>
  drop_na()
freq.table

a1 <- freq.table |>
  ggplot(aes(y = n, axis1 = Region, axis2 = Year)) +
  geom_alluvium(aes(fill = Income), width = 1 / 12) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "a1: geom_alluvium only")

a2 <- freq.table |>
  ggplot(aes(y = n, axis1 = Region, axis2 = Year)) +
  geom_alluvium(aes(fill = Income), width = 1 / 12) +
  geom_stratum(width = 1 / 12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) + scale_fill_brewer(palette = "Dark2") +
  labs(title = "a2: geom_alluvium, \n geom_stratum and geom_label")
a1 / a2
```



## geom_arc

**Package**

ggforce[@ggforce]

**Description**

Draw a circle or a segment of a circle.

**Understandable aesthetic**

*required aesthetics*

`x0` - starting coordinate of x-axis , `y0` - starting coordinate of x-axis, `r` - radius, `start`, `end`

*optional aesthetics*

`color`, `linewidth`, `linetype`, `alpha`, `lineend`

**The statistical transformation to use on the data for this layer**

`stat_arc`

**See also**

[geom_arc2](#arc2), [geom_arc_bar](#arcbar)

**Example**

```{r arc, warning=FALSE, message=FALSE}
library(ggforce)
ggplot() +
  geom_arc(aes(x0 = 0, y0 = 0, r = 8, start = 1, end = 8)) +
  geom_arc(aes(x0 = 0, y0 = 0, r = 8, start = 1, end = 5), col = "red", size = 2) +
  theme(aspect.ratio = 1)
```



## geom_arc_bar{#arcbar}

**Package**

ggforce[@ggforce]

**Description**

To draw pie chart and donut chart defining centre point, a radius and a start and end angle.

**Understandable aesthetic**

*required aesthetics*

`x0` - starting coordinate of x-axis , `y0` - starting coordinate of x-axis, `r` - radius, `start`, `end`

*optional aesthetics*

`color`, `linewidth`, `linetype`, `alpha`, `lineend`

**The statistical transformation to use on the data for this layer**

`stat_arc`

**See also**

[geom_arc](#arc), [geom_arc_bar](#arcbar)

**Example**


```{r, warning=FALSE, message=FALSE, fig.height=4, fig.width=4}
df <- data.frame(
  state = c(
    "A", "B", "C",
    "D", "E"
  ),
  focus = c(0.2, 0, 0, 0, 0),
  start = c(0, 1, 2, 3, 4),
  end = c(1, 2, 3, 4, 2 * pi),
  amount = c(4, 3, 1, 2, 5),
  stringsAsFactors = FALSE
)
ggplot(df) +
  geom_arc_bar(aes(
    x0 = 0, y0 = 0, r0 = 0, r = 1, amount = amount,
    fill = state, explode = focus
  ), stat = "pie") +
  scale_fill_brewer(palette = "Dark2") +
  theme(aspect.ratio = 1)
```




## geom_area{#area}

**Package**

ggplot2 [@ggplot2]

**Description**

Create an area plot. This cover the space between x-axis and line that connects the data points.

**Understandable aesthetics**

*required aesthetics*

`x`, `y`

*optional aesthetics*

`alpha`, `colour`, `fill`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)

**Example**

```{r area, warning=FALSE, message=FALSE}
a1 <- worldbankdata |>
  filter(Country == "Bangladesh") |>
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x = Year, y = Electricity)) +
  geom_area(alpha = 0.5) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_continuous(breaks = 2013:2021) +
  labs(title = "a1: geom_area only")

a2 <- worldbankdata |>
  filter(Country == "Bangladesh") |>
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x = Year, y = Electricity)) +
  geom_area(alpha = 0.5) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_continuous(breaks = 2013:2021) +
  geom_point(col = "red") +
  labs(title = "a2: geom_area \n and geom_point")
a1 | a2
```

## geom_arima

**Package**

ggdemetra 

**Example**

```{r}
library(ggdemetra)
 worldbankdata |>
  filter(Country == "Bangladesh") |>
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x = Year, y = Electricity)) +
  geom_line() + 
  #geom_sa(color = "#155692", message = FALSE) +
  geom_arima(geom = "label",
               x_arima = - Inf, y_arima = -Inf, 
               vjust = -1, hjust = -0.1,
               message = FALSE)
  
```

## geom_arrow{#arrow}

**Package**

metR [@metR]

**Description**

Draws directional arrows (like vectors) on a plot, which can represent directions or flows — such as wind directions, movement, or gradients. The arrow from (x, y) and pointing in the direction (dx, dy) (vector components).


**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
 `arrow,type`, `arrow.angle`, `arrow.length`, `arrow.ends`, `arrow.type`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
### Example
  
```{r warning=FALSE, message=FALSE,}
library(metR)
data <- tibble::tibble(
  x = c(10, 20, 30, 40, 50),           # Longitude or X-coordinates
  y = c(1, 2, 3, 4, 5),           # Latitude or Y-coordinates
  dx = c(1, 0, -1, 0, 1),         # Wind direction components (change in X)
  dy = c(1, -1, 0, 1, 0)          # Wind direction components (change in Y)
)

ggplot(data, aes(x = x, y = y)) +
  geom_point(color = "#1b9e77", size = 3) +  
  geom_arrow(aes(dx = dx, dy = dy), color = "#d95f02", size = 1, arrow.type = "closed") +
  labs(title = "Wind Directions at Different Locations", x = "Longitude", y = "Latitude")
```

## geom_ash{#ash}

**Package**

ggformula [@ggformula]



**Description**

Plot Average Shifted Histogram (ASH). The ASH is a nonparametric probability density estimator derived from a collection of histograms.

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
 `color`, `fill`, `bins`, `alpha`, `size`


**See also**

[geom_histogram](#histogram), [geom_density](#density)
  
**Example**


```{r}
#| warning: false
#| message: false
#| fig.width: 10
#| fig.height: 5
library(ggformula)
p1 <- worldbankdata |>
  filter(Income == "LM") |>
  ggplot(aes(x = Electricity)) +
   geom_ash(bins = 20, color = "#d95f02") +   labs(title="Average Shifted Histogram")
p2 <- worldbankdata |>
  filter(Income == "LM") |>
  ggplot(aes(x = Electricity)) +
  geom_histogram(aes(y = stat(density)), color = "black", fill = "gray") +
   geom_ash(bins = 20, color = "#d95f02") + labs(title = "Histogram and Average Shifted Histogram")
p1|p2
```

## geom_autodensity

## geom_autohistogram

## geom_autopoint

## geom_axis_hive