# A: geom_a  {#sec-a}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```


## geom_area{#area}

### Package

ggplot2 [@ggplot2]

### Description

Create an area plot. This cover the space between x-axis and line that connects the data points.

### Understandable aesthetics

alpha, colour, linetype, linewidth

### The statistical transformation to use on the data for this layer 

- `stat_identity`: Uses the y-values directly to define the are

### See also

[geom_line](#line), [geom_ribbon](#ribbon)

### Example

```{r area, warning=FALSE, message=FALSE}
area <- worldbankdata |>
  filter(Country == "Bangladesh") |> 
  filter(Year >= 2013 & Year <= 2021) |>
  ggplot(aes(x=Year, y=Electricity)) + 
  geom_area(alpha=0.5) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  scale_x_continuous(breaks = 2013:2021) + 
  labs(title = "geom_area only")

areapoint <- area + geom_point(col="red") + 
  labs(title = "geom_area and geom_point")
area | areapoint
```


## geom_abline{#abline}

**Package: ** ggplot2 [@R-ggplot2]

**Book: **

**Description: ** Draw a straight line ($Y=mX+c$) for a given slope ($m$)  and intercept ($c$).

**Understandable aesthetics:** alpha, colour, linetype, linewidth

**Statistics layer(s):**

**See also: ** [geom_point](#point), [geom_vline](#vline), [geom_hline](#hline)

**Example:**

```{r, fig.cap="Illustration of (A) geom_abline and (B) use of geom_point and geom_abline both",fig.height=5, fig.width=5}
abline <- ggplot(worldbankdata, aes(y = Cooking, x=Electricity)) +  geom_abline(intercept = 0, slope = 1) + 
  labs(title="A: `geom_abline` only") +
  theme(aspect.ratio = 1)

pointabline <- abline + 
  geom_point() + 
  theme(aspect.ratio = 1)

library(patchwork)
abline | pointabline
```
