# geom_c  {#sec-c}

```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
library(ggpattern)
data("worldbankdata")
```


## geom_col

### Package

ggplot2 [@ggplot2]

### Description

Create bar charts

### Understandable aesthetics

### The statistical transformation to use on the data for this layer

Before using `geom_col`, you need to create a summary table of counts/proportions or you can apply `geom_col` for a summary table.

`after_stat(count)`

`after_stat(prop)`

### See also

[geom_bar](#bar)

### Example

```{r, echo=FALSE}
worldbankdata |>
  filter(Year == 2021) |>
  group_by(Income) |>
  summarise(n = n()) |>
  ggplot(aes(x = Income, y = n)) +   geom_col()

```


## geom_col_pattern{#col_pattern}

### Package

ggpattern [@ggpattern]

### Description

Fill columns with a pattern. User can map a variable for pattern or set a pattern.

### Understandable aesthetics

`x`, `y`, `pattern`, `fill`, `colour`

### The statistical transformation to use on the data for this layer

None


### See also

[geom_line](#line), [geom_ribbon](#ribbon)

```{r, fig.cap="Illustration of geom_col_pattern"}
worldbankdata |>
  filter(Year == 2021) |>
  group_by(Income) |>
  summarise(n = n()) |>
  ggplot(aes(x = Income, y = n)) +   ggpattern::geom_col_pattern( pattern = 'stripe',
    fill    = 'white',
    colour  = 'black')
```


## geom_circle{#circle}

### Package

ggforce [@ggforce]

### Description

### Understandable aesthetics


**required aesthetics**

`x0` - starting coordinate of x-axis , `y0` - starting coordinate of x-axis, `r` - radius

**optional aesthetics**

`color`, `fill`, `linewidth`, `linetype`, `alpha`, `lineend`

### The statistical transformation to use on the data for this layer 

`stat_align`

### See also

[geom_mark_circle](#mark_circle), 
### Example

```{r, warning=FALSE, message=FALSE}
worldbankdata |>
  filter(Year == 2021) |>
ggplot(aes(y = Cooking, x=Electricity, col=Income)) + 
  geom_point() + 
  ggforce::geom_circle(aes(x0 = 26, y0 = 5, r = 20),
              inherit.aes = FALSE) + 
  theme(aspect.ratio = 1)
```

