# geom_e  {#sec-e}

```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
library(ggpattern)
data("worldbankdata")
```

## geom_errorbar{#errorbar}

### Package

ggplot2 [@ggplot2]

### Description

Plot a vertical interval defined by x, ymin and ymax.

### Understandable aesthetics

**required aesthetics**

`x` or `y`

`ymin` or `xmin` (y/x coordinate of the lower whisker)

`ymax` or `xmax` (y/x coordinate of the upper whisker)

**optional aesthetics**

`alpha`, `colour`, `group`, `linetype`, `linewidth`

### The statistical transformation to use on the data for this layer 

`stat_identity`

### See also

[geom_crossbar](#crossbar), [geom_dumbbell](#dumbbell)

### Example

```{r, warning=FALSE, message=FALSE, fig.height=5}
df <- worldbankdata |>
  group_by(Income) |>
  summarise(min = min(Electricity, na.rm=TRUE), max = max(Electricity, na.rm=TRUE), mean = mean(Electricity, na.rm=TRUE))
df
a1 <- ggplot(data=df, aes(x=Income, ymin=min, ymax=max)) + 
geom_errorbar(width=0.2, size=1, color="#d95f02") + 
  labs(title = "a1: geom_errorbar only")

a2 <- ggplot(data=df, aes(x=Income, ymin=min, ymax=max)) + 
  geom_errorbar(width=0.2, size=1, color="#d95f02") + 
  geom_point(data=df, mapping=aes(x=Income, y=mean), size=4, shape=21, fill="#1b9e77") +
  labs(title = "a2: geom_errorbar and geom_point")
a1|a2
```


## geom_errorbarh

### Package

ggplot2 [@ggplot2]

### Description

Plot a vertical interval defined by x, ymin and ymax.

### Understandable aesthetics

**required aesthetics**

`x` or `y`

`ymin` or `xmin` (y/x coordinate of the lower whisker)

`ymax` or `xmax` (y/x coordinate of the upper whisker)

**optional aesthetics**

`alpha`, `colour`, `group`, `linetype`, `linewidth`

### The statistical transformation to use on the data for this layer 

`stat_identity`

### See also

[geom_crossbar](#crossbar), [geom_dumbbell](#dumbbell)

### Example

```{r, warning=FALSE, message=FALSE, fig.height=5}
df <- worldbankdata |>
  group_by(Income) |>
  summarise(min = min(Electricity, na.rm=TRUE), max = max(Electricity, na.rm=TRUE), mean = mean(Electricity, na.rm=TRUE))
df
a1 <- ggplot(data=df, aes(x=Income, ymin=min, ymax=max)) + 
geom_errorbarh(width=0.2, size=1, color="#d95f02") + 
  labs(title = "a1: geom_errorbar only")

a2 <- ggplot(data=df, aes(x=Income, ymin=min, ymax=max)) + 
  geom_errorbarh(width=0.2, size=1, color="#d95f02") + 
  geom_point(data=df, mapping=aes(x=Income, y=mean), size=4, shape=21, fill="#1b9e77") +
  labs(title = "a2: geom_errorbar and geom_point")
a1|a2
```