# geom_f  {#sec-f}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
library(ggpattern)
data("worldbankdata")
```


## geom_function {#function}

### Package

ggplot2 [@ggplot2]

### Description

Computes and draws a function as a continuous curve.

### Understandable aesthetics


**required aesthetics**

`x`

`y`

**optional aesthetics**

`alpha`, `colour`, `group`, `linetype`, `linewidth`


### The statistical transformation to use on the data for this layer


`stat_`prefix


### See also

[geom_density](#density)

### Example

```{r, warning=FALSE, message=FALSE, fig.height=5, fig.width=5}
ggplot() + 
  geom_function(fun = ~ 0.5*exp(-abs(.x)))

```

## geom_freqpoly {#freqpoly}

### Package

ggplot2 [@ggplot2]

### Description

Visualise the spread of a single continuous variable by partitioning the x-axis into bins and mapping the frequency of observations within each bin.

### Understandable aesthetics

**required aesthetics**

`x`

`y`

**optional aesthetics**

`alpha`, `colour`, `group`, `linetype`, `linewidth`


### The statistical transformation to use on the data for this layer


`stat_bin` for a continuous x variable

`stat_count` for a discrete x variable


### See also

[geom_density](#density)

### Example

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}
worldbankdata |>
  ggplot(aes(x=Electricity, col=Income)) + 
  geom_freqpoly()
```
