# geom_h  {#sec-h}

```{r, echo=FALSE,warning=FALSE,message=FALSE}
library(drone)
library(tidyverse)
library(patchwork)
data(worldbankdata)
```

## geom_hline{#hline}


### Package

ggplot2 [@ggplot2]

### Description

Draw a horizontal line ($Y=c$) for a given value of $c$, which is known as `yintercept`.

### Understandable aesthetics

Unlike most other geoms, `geom_hline` does not depend on the x and y variables that we map for the main plot. `geom_hline` has its own independent characteristics: `yintercept`.   The yintercept can be passed either as a arguments or aesthetic.

### Statistics layer(s)

None

### See also

[geom_point](#point), [geom_vline](#vline), [geom_hline](#hline)

### Example


```{r hline2, fig.cap="Illustration of (A) geom_hline and (B) use of geom_point and geom_hline both", warning=FALSE,message=FALSE}
a1 <- ggplot(worldbankdata, aes(y = Cooking, x= Electricity)) + geom_hline(yintercept = 50) + 
  labs(title="a1: `geom_hline` only") +
  theme(aspect.ratio = 1)

a2 <- ggplot(worldbankdata, aes(y = Cooking, x=Electricity)) + 
  geom_point() + 
  geom_hline(yintercept = 50) + 
  labs(title="a2: `geom_point +\n geom_hline` both") +
  theme(aspect.ratio = 1)
a1 | a2
```

