# Introduction

## What is data visualisation?

To explain the idea I use the following dataset.


```{r}
set.seed(2024)
var1 <- rnorm(30)
var2 <- factor(rep(c(1, 2, 3), each=10))
toydata <- data.frame(var1, var2)
head(toydata) 
```

```{r}
library(ggplot2)
ggplot(toydata, aes(x=var2, y=var1, col=var2)) +
  geom_point()
```

## What did we do in making a plot to data visualisation?




## What is `geom`?




Below are four methods that I used to visualise the distribution of var1 by var 2.

```{r}
library(patchwork)
library(ggridges)
p <- ggplot(toydata, aes(x=var2, y=var1, col=var2))
p1 <- p + geom_point() + ggtitle("A")
p2 <- p + geom_boxplot() + ggtitle("B")
(p1|p2)
```


## Data

```{r}
library(drone)
library(tibble)
data(worldbankdata)
worldbankdata
```

## Data description

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(visdat)
vis_dat(worldbankdata) + 
  scale_fill_brewer(palette = "Dark2")
```

```{r}
library(naniar)
gg_miss_upset(worldbankdata) 
```

## Packages use for data wrangiling and |> operator


## R packages with geom implementation

1. ggplot2 [@ggplot2]

2. ggpattern [@ggpattern]

3. ggforce [@ggforce]

4. ggalluvial [@ggalluvial]

5. ggbump [@ggbump]

6. ggridges [@ggridges]

7. ggalt [@ggalt]

