# geom_l  {#sec-l}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```

## geom_label

**Package**

ggplot2 [@ggplot2]

**Description**

Labelling plots

**Understandable aesthetics**

*Required aesthetics*

`x`, `y`, `label`


*Optional aesthetics*

`alpha`, `angle`, `colour`, `family`, `fontface`, `group`, `hjust`,  `lineheight`, `size`, `vjust`


**See also**

[geom_text](#text)

**Example**

```{r area, warning=FALSE, message=FALSE}
a1 <- worldbankdata |>
  filter(Income == "L" | Income =="H") |> 
  filter(Year == 2021) |>
  ggplot(aes(x = Cooking, y = Electricity, label = Income)) + 
  geom_label(aes(fill = factor(Income)), colour = "white", fontface = "bold", alpha=0.5) + theme(aspect.ratio = 1) + labs(title = "a1: geom_label only") 
a2 <- worldbankdata |>
  filter(Income == "L" | Income =="H") |> 
  filter(Year == 2021) |>
  ggplot(aes(x = Cooking, y = Electricity, label = Income)) + 
  geom_point(aes(col = Income)) +  theme(aspect.ratio = 1) + 
  labs(title = "a2: geom_point only") 
a1|a2
```


## geom_line{#line}


**Package**

ggplot2 [@ggplot2]

**Description**

Connects data in order of the variable on the x axis.

**Understandable aesthetics**



*required aesthetics*
  
`x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`



**See also**

[geom_path](#path)
  
**Example**

```{r, warning=FALSE, message=FALSE}
a1 <- worldbankdata |>
  filter(Country == "Sri Lanka") |>
  ggplot(aes(x=Year, y=Cooking)) + 
  geom_line() + ggtitle("geom_line only")
a2 <- worldbankdata |>
  filter(Country == "Sri Lanka") |>
  ggplot(aes(x=Year, y=Cooking)) + 
  geom_line() + 
  geom_point() +
  ggtitle("geom_line and geom_point")
a1|a2
```

## geom_linerange


**Package**

ggplot2 [@ggplot2]

**Description**

Representing a vertical interval defined by x, ymin and ymax

**Understandable aesthetics**

*required aesthetics*
  
`x` or `y`,

`ymin` or `xmin`,

`ymax` or `xmax`

*optional aesthetics*
  
`alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_crossbar](#crossbar), [geom_errorbar](#errorbar), [geom_pointrange](#pointrange)
  
**Example**


```{r}
worldbankdata |>
  group_by(Region) |>
  summarise(min = min(Cooking, na.rm = TRUE), max=max(Cooking, 
                                                      na.rm = TRUE)) |>
  ggplot(aes(x=Region)) +
  geom_linerange(aes(ymin = min, ymax = max)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
