# O  {#sec-o}

```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```

## geom_outlier {#outlier}

**Package**

ggdemetra [@ggdemetra]

**Description**

Function to add directly to the plot the outliers used in the pre-adjustment process of the seasonal adjustment.

**Understandable aesthetics**

*required aesthetics*
  
`date`

`y`

Note: frequency must be equal to 12, 6, 4 or 2

*optional aesthetics*
  
`first_date`, `last_date`, `coefficients`, `digits`, `show.legend`, `inherit.aes`


**See also**

[geom_text](#text), [geom_label](#label)
[geom_text_repel](#text_repel), [geom_label_repel](#label_repel)
  
**Example**

```{r, warning=FALSE, message=FALSE}
#install.packages("RJDemetra")
#install.packages("ggdemetra")
library(RJDemetra)
library(ggdemetra)
ipi_c_eu <- window(ipi_c_eu, start = c(2000, 1), end = c(2010, 12))
ipi_c_eu_df <- ts2df(ipi_c_eu)
p1 <- ggplot(data = ipi_c_eu_df, mapping = aes(x = date, y = FR)) +
    geom_line() + ggtitle("Without geom_outlier")
p2 <- ggplot(data = ipi_c_eu_df, mapping = aes(x = date, y = FR)) +
    geom_line() + geom_outlier(geom = "label_repel") + ggtitle("With geom_outlier")
p1/p2
```

## geom_outline {#outline}


**Package**

ggplot2 [@ggplot2]

**Description**

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
**Example**
  


## geom_outline_point{#outline_point}


**Package**

ggplot2 [@ggplot2]

**Description**

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
**Example**
  


##  geom_overhang_seats{#overhang_seats}


**Package**

ggparliament [@ggparliament]

**Description**

Draw overhang seats in mixed-member proportional (MMP) electoral systems

**Understandable aesthetics**

*required aesthetics*
  
  `expr`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
  
**Example**

```{r}
#devtools::install_github("zmeers/ggparliament")
library(ggparliament)
sriLanka <- tibble(
  year = 2024,
  seats = c(64, 63, 311, 193),
  government = c(0, 0, 1, 1),
  colour = c("red", "blue", "green", "orange"),
  party = c("SLPFA",
            "SJB",
            "NPP",
            "TNA"))

sl_data <- parliament_data(
  election_data = sriLanka,
  parl_rows = 11,
  party_seats = sriLanka$seats,
  type = "horseshoe")

sl_data$overhang_seats <- rep(
  c(1, 0, 1, 0, 1, 0, 1, 0),
  c(295, 16, 11, 182, 3, 61, 3, 60)
)
ggplot(sl_data, aes(x, y, colour = party)) +
  geom_parliament_seats() +
  geom_overhang_seats(overhang_seats == 0.2) +
  theme_ggparliament() +
  scale_colour_manual(values = c("red", "blue", "green", "orange"))

```


