# geom_q  {#sec-q}

```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```

## geom_qq{#qq}

**Package**

ggplot2 [@ggplot2]

**Description**

Draws quantitle-quantile plot.

**Understandable aesthetics**

*required aesthetics*
  
 `sample`


*optional aesthetics*
  
  `group`, `x`, `y`


**See also**

[geom_qq_line](#qq_line)
  
**Example**


```{r}
worldbankdata |>
  ggplot(aes(sample = Cooking)) +
  geom_qq()
  
```

## geom_qq_line{#qq_line}

**Package**

ggplot2 [@ggplot2]

**Description**

Computes the slope and intercept of the line connecting the points at specified quartiles of the theoretical and sample distribution in the quantitle-quantile plot. This geom should be used along with geom_qq to plot to be meaningful.

**Understandable aesthetics**

*required aesthetics*
  
 `sample`


*optional aesthetics*
  
  `group`, `x`, `y`


**See also**

[geom_qq_line](#qq_line)
  
**Example**


```{r, warning=FALSE, message=FALSE}
a1 <- worldbankdata |>
  ggplot(aes(sample = Cooking)) +
  geom_qq_line()  + ggtitle("geom_qq_line only")
a2 <- worldbankdata |>
  ggplot(aes(sample = Cooking)) +
  geom_qq_line() + geom_qq() + ggtitle("geom_qq_line and geom_qq")
a1|a2
```



## geom_qquantile{#quantile}

**Package**

ggplot2 [@ggplot2]

**Description**

Fits and draw quantile regression lines. Quantile regression models the relationship  between independent variables and the percentiles of the dependent variable


**Understandable aesthetics**

*required aesthetics*
  
 `x`, `y`


*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`, `weight`, `quantile`, `method`


**See also**

[geom_boxplot](#boxplot)
  
**Examples**

Example 1

```{r, warning=FALSE, message=FALSE}
a1 <- worldbankdata |>
  ggplot(aes(y=Cooking, x = Electricity)) + 
  geom_quantile() + ggtitle("geom_quantile only")
a2 <- worldbankdata |>
  ggplot(aes(y=Cooking, x = Electricity)) + 
  geom_quantile() + 
  geom_point() +
  ggtitle("geom_quantile and geom_point")
a1|a2
```

Example 2

```{r, warning=FALSE, message=FALSE}
q <- seq(0.05, 0.95, by = 0.05)
a3 <- worldbankdata |>
  ggplot(aes(y=Cooking, x = Electricity)) + 
  geom_quantile(method = "rqss") + 
  ggtitle("geom_quantile with method rqss")
a4 <- worldbankdata |>
  ggplot(aes(y=Cooking, x = Electricity)) + 
  geom_quantile(method = "rqss") + 
  geom_point() +
  ggtitle("geom_quantile with \n method rqss and geom_point")
a3|a4
```