# R {#sec-r}

```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```



## geom_raster{#raster}

**Package**

ggplot2 [@ggplot2]

**Description**



**Understandable aesthetics**

*required aesthetics*


*optional aesthetics*



**See also**

[geom_tile](#tile), [geom_rect](#rect)

**Example**


## geom_rect

**Package**

ggplot2 [@ggplot2]

**Description**



**Understandable aesthetics**

*required aesthetics*


*optional aesthetics*



**See also**

[geom_tile](#tile), [geom_rect](#rect)

**Example**

## geom_ribbon

**Package**

ggplot2 [@ggplot2]

**Description**



**Understandable aesthetics**

*required aesthetics*


*optional aesthetics*



**See also**


**Example**

## geom_rub

**Package**

ggplot2 [@ggplot2]

**Description**



**Understandable aesthetics**

*required aesthetics*


*optional aesthetics*



**See also**


**Example**

```{r}

```

## geom_rect


**See also**

[geom_tile](#tile), [geom_raster](#raster)

## geom_raster


**See also**

[geom_tile](#rect), [geom_tile](#tile)