# geom_t  {#sec-t}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```



## __geom_text__

__Package__

ggplot2 [@ggplot2]

__Description__

Text geoms are useful for labeling plots. They can be used by themselves as scatterplots or in combination with other geoms, for example, for labeling points or for annotating the height of bars. geom_text() adds only text to the plot.

__Understandable aesthetics__

_required aesthetics_

x, y

_optional aesthetics_

stat , position  , size

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
drop_na(worldbankdata) %>% 
  filter(Code %in% c('AFG', 'AGO', 'BEN', 'BFA', 'BGD', 'BOL', 'BWA')) %>% 
  ggplot(aes(x = Cooking, y = Electricity, label = Income)) + 
  geom_point(aes(color = Income), size = 1) +
  geom_text(size = 3) +  
  labs(title = "",x = "Cooking", y = "Electricity")  +  
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10))
```

## __geom_text_repel__

__Package__

ggrepel [@ggrepel]

__Description__

geom_text_repel adds text directly to the plot

__Understandable aesthetics__

_required aesthetics_

x, y

_optional aesthetics_

stat , position  , size

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
library(ggrepel)
ggplot(mtcars, aes(x = wt, y = mpg, label = rownames(mtcars))) +
  geom_text_repel() +  
  labs(title = "",x = "Weight (1000 lbs)", y = "Miles/(US) gallon")  +  
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10))
```

## __geom_tile__

__Package__

ggplot2 [@ggplot2]

__Description__

geom_text_repel adds text directly to the plot

__Understandable aesthetics__

_required aesthetics_

x, y

_optional aesthetics_

stat , position  , size

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
drop_na(worldbankdata) %>% 
  filter(Code %in% c('AFG', 'AGO', 'BEN', 'BFA', 'BGD', 'BOL', 'BWA')) %>% 
  ggplot( aes(x = Cooking, y = Electricity)) + geom_point(aes(col = Code)) +
  geom_tile(aes(fill = Code)) +  
  labs(title = "",x = "Cooking", y = "Electricity")  +  
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10))
```

## __geom_text_cooks__

__Package__

ggxmean [@ggxmean]

__Description__

Returns a scatter plot with points that are labeled.

__Understandable aesthetics__

_required aesthetics_

x, y

_optional aesthetics_

position  , size, digits, check_overlap

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
data <- data.frame(
  x = 1:20,  
  y = 3 + 2 * (1:20) + rnorm(20, mean = 0, sd = 2))

data %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_lm() +
  geom_text_cooks(check_overlap = TRUE, digits = 1)  +  
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10))
```

## __geom_text_coordinate__

__Package__

ggxmean [@ggxmean]

__Description__

Returns a scatter plot with points that are labeled.

__Understandable aesthetics__

_required aesthetics_

x, y

_optional aesthetics_

position  , size, check_overlap, nudge_x

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
data <- data.frame(
  x = 1:20,  
  y = 3 + 2 * (1:20) + rnorm(20, mean = 0, sd = 2))

data %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_text_coordinate(check_overlap = TRUE, nudge_x = .3)  +  
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10))
```

## __geom_text_leverage__

__Package__

ggxmean [@ggxmean]

__Description__

Returns a scatter plot with points that are labeled.

__Understandable aesthetics__

_required aesthetics_

x, y

_optional aesthetics_

position  , size, check_overlap, nudge_x

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
drop_na(worldbankdata) %>% 
  filter(Code %in% c('AFG', 'AGO', 'BEN', 'BFA', 'BGD', 'BOL', 'BWA', 'TLS')) %>% 
  ggplot(aes(x = Electricity, y = Cooking)) +
  geom_point() +
  geom_text_coordinate(check_overlap = TRUE, nudge_x = .3)  +  
  labs(title = "",x = "Cooking", y = "Electricity")  + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10))
```

