# geom_t  {#sec-t}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```



## __geom_text__

__Package__

ggplot2 [@ggplot2]

__Description__

Labeling plots. 

__Understandable aesthetics__

_required aesthetics_

`x`, `y`

_optional aesthetics_

`stat` , `position`  , `size`

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=5}
p1 <- drop_na(worldbankdata) |>
  filter(Code %in% c('AFG', 'AGO', 'BEN', 'BFA', 'BGD', 'BOL', 'BWA')) |>
  ggplot(aes(x = Cooking, y = Electricity, label = Income)) + geom_text(size = 3) + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("geom_text only")
p2 <- drop_na(worldbankdata) |>
  filter(Code %in% c('AFG', 'AGO', 'BEN', 'BFA', 'BGD', 'BOL', 'BWA')) |>
  ggplot(aes(x = Cooking, y = Electricity, label = Income)) + 
  geom_point(aes(color = Income)) +
  geom_text(size = 3) + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("geom_point and geom_text only")
p1|p2
```

## __geom_text_repel__

__Package__

ggrepel [@ggrepel]

__Description__

Repulsive textual annotations.

__Understandable aesthetics__

_required aesthetics_

`x, y

_optional aesthetics_

stat , position  , size

__Example__

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=5}
library(ggrepel)
p1 <- ggplot(mtcars, aes(x = wt, y = mpg, label = rownames(mtcars))) +
  geom_text_repel() +  
  labs(title = "",x = "Weight (1000 lbs)", y = "Miles/(US) gallon") + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("geom_text_repel only")
p2 <- ggplot(mtcars, aes(x = wt, y = mpg, label = rownames(mtcars))) +
  geom_point() +
  geom_text_repel() +  
  labs(title = "",x = "Weight (1000 lbs)", y = "Miles/(US) gallon") + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("geom_text_repel and geom_point")
p1|p2
```
