# geom_x  {#sec-x}


```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```


## geom_x_label

### Package

ggxmean [@ggxmean]

## geom_x_line

### Package

ggxmean [@ggxmean]


## geom_x_mean

### Package

ggxmean [@ggxmean]

## geom_x_mean_label

### Package

ggxmean [@ggxmean]


## geom_x_median

### Package

ggxmean [@ggxmean]

## geom_x_percentile

### Package

ggxmean [@ggxmean]

## geom_x_quantile

### Package

ggxmean [@ggxmean]

## geom_xmax

### Package

ggxmean [@ggxmean]

## geom_xmin

### Package

ggxmean [@ggxmean]

## geom_xy_means


### Package

```{r}
# install.packages("devtools")
#devtools::install_github("EvaMaeRey/ggxmean")
```

ggxmean [@ggxmean]

### Description

Place point at mean of x and mean of y

### Understandable aesthetics

**required aesthetics**
  
`x`, `y`

### The statistical transformation to use on the data for this layer 



### See also

[geom_point](#point)
  


### Example 

```{r}
library(ggxmean)
a1 <- worldbankdata |>
  ggplot(aes(x = Income, y = Cooking)) + 
  geom_xy_means(na.rm=TRUE, col="red", size=4) + 
  ggtitle("a1: geom_xy_means only")
a2 <- worldbankdata |>
  ggplot(aes(x = Income, y = Cooking)) + 
  geom_point(alpha=0.5) +
  geom_xy_means(na.rm=TRUE, col="red", size=4) + 
  ggtitle("a2: geom_points and geom_xy_means")
a1|a2
```

## geom_xy_xymean

### Example 

```{r, warning=FALSE, message=FALSE}
library(ggxmean)
worldbankdata |>
  ggplot(aes(x = Income, y = Cooking)) + 
  geom_xy_xymean(na.rm=TRUE, size=3) 

```