# Y  {#sec-y}

```{r, message=FALSE, warning=FALSE,echo=FALSE}
library(tidyverse)
library(drone)
library(patchwork)
data("worldbankdata")
```



##geom_y_line{#y_line}

**Package**

ggxmean [@ggxmean]

**Description**

Create horizontal lines representing the specified value of the y variable across the x values in the data.

**Understandable aesthetics**

*required aesthetics*
  
`x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_ydiff](#ydiff), [geom_line](#line)
  
**Example**

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

library(ggxmean)
p1 <- worldbankdata |> 
  filter(Country == "Angola") |>
  ggplot(mapping = aes(x = Cooking, y = Electricity)) +
geom_point()  + ggtitle("without geom_y_line")
p2 <- worldbankdata |> 
  filter(Country == "Angola") |>
  ggplot(mapping = aes(x = Cooking, y = Electricity)) +
geom_point() + geom_y_line(alpha = .2) + 
  ggtitle("with geom_y_line")
p1|p2
```


## geom_y_mean{#y_mean}

**Package**

ggxmean [@ggxmean]

**Description**

Draw a horizontal line at the mean of y-variable.

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
[geom_y_line](#y_line)
  
**Example**

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

library(ggxmean)
p1 <- worldbankdata |> 
  filter(Country == "Angola") |>
  ggplot(mapping = aes(x = Cooking, y = Electricity)) +
geom_point()  + ggtitle("without geom_y_mean")
p2 <- worldbankdata |> 
  filter(Country == "Angola") |>
  ggplot(mapping = aes(x = Cooking, y = Electricity)) +
geom_point() + geom_y_mean(colour="#d95f02") + 
  ggtitle("with geom_y_mean")
p1|p2
```


##geom_ydiff{#ydiff}

**Package**

ggplot2 [@ggplot2]

**Description**

**Understandable aesthetics**

*required aesthetics*
  
  `x`

`y`

*optional aesthetics*
  
  `alpha`, `colour`, `group`, `linetype`, `linewidth`


**See also**

[geom_line](#line), [geom_ribbon](#ribbon)
[geom_y_line](#y_line)
  
**Example**

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

library(ggxmean)
p1 <- worldbankdata |> 
  filter(Country == "Angola") |>
  ggplot(mapping = aes(x = Cooking, y = Electricity)) +
geom_point()  + ggtitle("without geom_ydiff")
p2 <- worldbankdata |> 
  filter(Country == "Angola") |>
  ggplot(mapping = aes(x = Cooking, y = Electricity)) +
geom_point() +
  geom_y_mean(col="#d95f02")+ggxmean:::geom_ydiff(colour="#1b9e77") + 
  ggtitle("with geom_ydiff")
p1|p2
```